Differential Expression - MSSM-Penn-Pitt - DLPFC - Dx_Sex

### 2020-07-30 individual-cohorts/MSSM-Penn-Pitt_DLPFC_DE.Rmd
fix undefined columns

# Set variable class
FactorCovariates <- c("Individual_ID", "Institution", "LibraryBatch", "Dx_Sex", "RibozeroBatch", "FlowcellBatch")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)

>>>>

# Set variable class
FactorCovariates <- c("Individual_ID", "Institution", "LibraryBatch", "Dx", "Reported_Gender", "RibozeroBatch", "FlowcellBatch")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
